### 2024-02-21 documentation/thesis/thesis_abstract.tex
.

A passive shimming process is typically used to adjust the B0 field
afterwards. This is complex and time-consuming and requires manual
corrections to the magnets used. To avoid this process, magnets can be
systematically measured in advance. Sensor accuracy and repeatability
data acquisition, storage and subsequent analysis play an important role
in this methodology.

>>>>

A passive shimming process is typically used to adjust the B0 field
afterwards. This is complex and time-consuming and requires manual
corrections to the magnets used. To avoid this process, magnets can be
systematically measured in advance. Data acquisition, storage and
subsequent analysis of the recorded data play an important role in this
method. It is also essential that the sensors used are repeatable and
work with the specified accuracy, which must also be characterised in
advance for this purpose.
